Group 9 Presentation

### 2021-12-08 presentation.Rmd
BAGGING FIXED NOW, SVM IS BROKEN

---
title: "Group 9 Presentation"
author: "Henrique, Oriana, Jorie"
date: "12/4/2021"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

@@

## Group 9

Heart Disease
Oriana Meldrum, Henrique Rio, Jorie Alvis

@@

LDA_model
```

@@

confm2<-table(predicted=rf,True=true)
kable(confm2)

@@

- ST_Slope
-

@@

```{r SVM}
SVM_radial = svm(HeartDisease~., data=train, kernel="radial", gamma=0.25, cost=0.4)

table(predicted=preds,true=test$HeartDisease)

paste("Accuracy", acc)
```

@@

@@

Oriana's Lasso

## KNN

@@

#Confusion Matrix
predict_bag <- predict(bagging, newdata = test)
predicted_bag <- ifelse(predict_bag>0.5,1,0)
confm_bag<-table(predict_bag,test$HeartDisease)

@@

- What method should be choosen?

>>>>

---
title: "Group 9 Presentation"
subtitle: "Heart Disease Classification"
author: "Henrique Magalhaes Rio , Oriana Meldrum, Jorie Alvis"
date: "12/8/2021"
output:
  slidy_presentation: default
  ioslides_presentation: default
  beamer_presentation: default
---

@@

@@

LDA_model
```
## KNN

#Confusion Matrix
predict_bag <- predict(bagging, newdata = test)
predicted_bag <- ifelse(predict_bag>0.5,1,0)
confm_bag<-table(predict_bag,test$HeartDisease,)

@@

confm2<-table(predicted=rf,True=true)
confm2

@@

## Random Forest Plot

@@

@@

- Tuning Parmeters Choosen= 600 trees, shrinkage=0.01, interaction= 2.

@@

```{r SVM}

@@

SVM_radial = svm(HeartDisease~., data=train, kernel="radial", gamma=0.25, cost=0.4)

table(preds,test$HeartDisease)

paste("the overall fraction of correct predictions in the test dataset is :", acc)
```

@@

- What method would be the best?
